Pre-processing high frequency animal tracking data

### 2020-09-22 11_residence_patch.Rmd
add res patch code

## Residence patches and their construction

@@

>>>>

---
output: html_document
editor_options: 
  chunk_output_type: console
---
## Residence patches and their construction

@@

## Prepare libraries {-}

```{r prep_libs_02_01}
library(data.table)
library(atlastools)
library(ggplot2)
```

## Read data and classify

```{r}
# read in the data
data <- fread("data/data_sim.csv")[5000:10000, ]
data[, id := "a"]

# make residence patch
patch <- atl_res_patch(data, 
                       buffer_radius = 0.0001, 
                       lim_spat_indep = 0.02, 
                       lim_time_indep = 3)
# get spatial representation
patch_sf <- atl_patch_summary(patch_data = patch, 
                              which_data = "spatial", 
                              buffer_radius = 0.01)

# get summary data
patch_summary <- atl_patch_summary(patch_data = patch,
                                   which_data = "summary")
```

## Plot classified residence patches

```{r}
plot_patches <- ggplot()+
  geom_sf(data = patch_sf,
          colour = "NA",
          aes(fill = duration),
          show.legend = FALSE)+
  geom_point(data = data,
             aes(x, y),
             size = 0.1,
             alpha = 0.1)+
  geom_point(data = patch_summary,
             aes(x_median + 0.5, y_median),
             size = 5,
             shape = 21,
             fill = "grey")+
  annotate(geom = "text",
           x = patch_summary$x_median + 0.5, 
           y = patch_summary$y_median + 0.02,
           label = patch_summary$patch,
           col = "red")+
  annotate(geom = "text",
           x = patch_summary$x_median, 
           y = patch_summary$y_median + 0.02,
           label = patch_summary$patch,
           col = "red")+
  annotate(geom = "text",
           x = c(0.5, 1.1),
           y = 1,
           label = sprintf("(%s)", c("a", "b")),
           fontface = "bold")+
  geom_path(data = patch_summary,
            aes(x_median + 0.5, y_median),
            colour = "darkblue",
            arrow = arrow(angle = 10, 
                          type = "closed"))+
  scale_fill_viridis_c()+
  theme_void()

plot_patches

# save figure
ggsave(plot_patches, 
       filename = "figures/fig_residence_patch.png",
       width = 185, height = 185 * 2 / 3, units = "mm")
```
